Figure 2 - Overview heatmaps for IP-MS and ChIP

### 2024-08-06 ms_figure_2_overview-heatmaps.Rmd
reorder panels in Fig2 and label HOT TFs in ChIP heatmaps

# specify ChIP-seq experiments for which to show labels
selLabels <- c("Untagged")
stopifnot(all(selLabels %in% colnames(m)))

@@

cowplot::plot_grid(
    hm_peaksEnr,
    hm_peaksBin,
    hm_150,
    hm_500,
    nrow = 2,
    labels = c("A", "B", "C", "D"),
    align = "v",
    axis = "b"
)
```

>>>>

# specify ChIP-seq experiments for which to show labels
selLabels <- c(hot_tfs, "Untagged")
stopifnot(all(selLabels %in% colnames(m)))

@@

cowplot::plot_grid(
    hm_150,
    hm_500,
    hm_peaksEnr,
    hm_peaksBin,
    nrow = 2,
    labels = c("A", "B", "C", "D"),
    align = "v",
    axis = "b"
)
```
